\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-07 paper/paper 2/dc-2015.tex
2.3

	\caption{Simple Constraints which are not Expressible in DL)}

@@

%\emph{Complex constraints} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
\emph{Complex constraints} of the constraint type \emph{context-specific exclusive or of property groups} (\emph{R-13}) 
restrict individuals of given classes to have all properties of exactly one of multiple mutually exclusive property groups.
\emph{Publications}, e.g., are either identified by an \emph{ISBN} and a title (for books) or by an \emph{ISSN} and a title (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}. 
As \emph{The-Great-Gatsby} is a \emph{publication} with an \emph{ISBN} and a title without an \emph{ISSN}, 
\emph{The-Great-Gatsby} is considered as a valid \emph{publication}.
The \emph{complex constraint} is generically expressible by DL:
%This \emph{complex constraint} is expressible specifically by \emph{ShEx} and generically by DL (and can therefore be mapped to the \emph{RDF-CV} \cite{BoschEckert2015-2}).

@@

%Even though, tools may generate \emph{generic constraints} automatically, this 
The DL statements demonstrate that the \emph{complex constraint} 
is composed of many other \emph{complex} (e.g. \emph{minimum and maximum qualified cardinality restrictions}) and \emph{simple constraints} (e.g. constraints on sets).
As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR)} are frequently used \emph{complex constraints},
we propose to simplify them as \emph{simple constraints} in terms of syntactic sugar.
As a consequence, the \emph{context-specific exclusive or of property groups} \emph{complex constraint} is represented as a \emph{generic constraint} by means of the \emph{RDF-CV} more intuitively and concisely (Table \ref{tab:simplified-complex-constraints}).

@@

\begin{table}[H]
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Simplified Complex Constraints}
	\label{tab:simplified-complex-constraints}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
class & Publication & - & - & E, F & XOR \\
class & E & - & - & A, B & intersection \\
class & F & - & - & C, D & intersection \\
property & A & isbn & - & string & = & 1 \\
property & B & title & - & string & = & 1 \\
property & C & issn & - & string & = & 1 \\
property & D & title & - & string & = & 1 \\
		\end{tabular}
\end{table}

>>>>

	\caption{Simple Constraints which are not Expressible in DL}

@@

%\emph{Complex constraints} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
Complex constraints of the constraint type \emph{context-specific exclusive or of property groups} (\emph{R-13}) restrict individuals of given classes to have all properties of exactly one of multiple mutually exclusive property groups. Publications, e.g., are either identified by an \emph{ISBN} and a title (for books) or by an \emph{ISSN} and a title (for periodical publications), but it should not be possible to assign both identifiers to a given publication. As \emph{The-Great-Gatsby} is a publication with an \emph{ISBN} and a title without an \emph{ISSN}, \emph{The-Great-Gatsby} is considered as a valid publication. This complex constraint is generically expressible in DL:
%This \emph{complex constraint} is expressible specifically by \emph{ShEx} and generically by DL (and can therefore be mapped to the \emph{RDF-CV} \cite{BoschEckert2015-2}).

@@

%Even though, tools may generate \emph{generic constraints} automatically, this 
The DL statements demonstrate that the complex constraint is composed of many other complex constraints (e.g., \emph{minimum and maximum qualified cardinality restrictions}) and simple constraints (e.g., constraints on sets). As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR)} are frequently used complex constraints, we propose to simplify them as simple constraints in terms of syntactic sugar. As a consequence, the \emph{context-specific exclusive or of property groups} complex constraint is represented as a generic constraint by means of the RDF-CV more intuitively and concisely (see Table \ref{tab:simplified-complex-constraints}).

@@

\begin{table}[H]
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Simplified Complex Constraints}
	\label{tab:simplified-complex-constraints}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
class & Publication & - & - & E, F & XOR of property groups & - \\
class & E & - & - & A, B & intersection & - \\
class & F & - & - & C, D & intersection & - \\
property & A & isbn & - & string & = & 1 \\
property & B & title & - & string & = & 1 \\
property & C & issn & - & string & = & 1 \\
property & D & title & - & string & = & 1 \\
		\end{tabular}
\end{table}
